The classical mutual information in mean-field spin glass models

### 2015-12-18 prb_resub/referee_response/response.txt

REFEREE:
-------

	(6). The authors only focused on the result at n=2. It would be	interesting if the authors mention the n-dependence of 
	the result. Especially, the limit n=1 would give a nontrivial result and is interesting. I expect that it wouldn't 
	be difficult to analyze the replica symmetric solution.

RESPONSE:
========

	We thank the referee for asking about this point. In fact we thought about investigating the analytic continuation 
	n->1 to obtain the Shannon Renyi entropy and mutual information. The referee question is interesting especially 
	in order to compare with the results for the clean infinite range Ising model obtained in Wilms et al. 
	It has been shown in fact in ... that the Shannon mutual information is O(1) (i.e., not extensive) at any temperature 
	except for the critical point at beta=1 whete it diverges logarithmically with system size.

	Following the referee suggestion we now provide results for the analytic continuation n->1. In the new version of 
	the manuscript in section IV B we discuss the analytic continuation for the paramagnetic replica symmetric case, 
	although this could be done as well in the replica symmetry broken region of the phase diagram.

	From the solution we observe that in the limit of infinite temperature one has

### 2015-12-20 sk_model_v20.tex
20/12/2015

In this section we present the solution of the S-K model on the booklet, using 
the replica symmetric (RS) approximation. In subsection~\ref{para-section} we focus 
on the high temperature phase, where this approximation is exact, and the 
behavior of the model is fully determined by the diagonal part of the overlap 
tensor $q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec} for its 
definition). The generic structure of $q_{\gamma\gamma'}^{rr'}$ 
within the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us 
to determine the critical temperature of the paramagnetic-glassy transition. 
For simplicity, here and in the following sections we restrict ourselves to zero 
magnetic field ($h=0$ in Eq.~\eqref{SK-ham}), and to $J_0=0$ in 
Eq.~\eqref{quenched-distr}.

@@

\beta^2\Big(\frac{n}{4}-\frac{q_0^2}{4}(n^2-n)
+\frac{\omega}{2}q_0n^2-q_0n\Big)\\

@@

(\omega,n,\beta)]/\partial q_0=0$. The saddle point equation reads 
where we used that 

@@

\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)= 
\frac{1}{2}\Gamma(n,n/2)\\
+\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\frac{n}{2}-1}\frac{\Gamma(n+1)}
{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0 \big(\frac{n}{2}-k\big)^2}

@@

Clearly, for two independent copies of the S-K model, i.e., $\omega=0$,  
Eq.~\eqref{saddle-high-t} gives $q_0=0$ for $\beta\le1$, whereas 
one has $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$, $q_0$ 
is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle_ht}. For $\beta=0$ it 
is $q_0=\omega$ (straight line in the Figure). In the low-temperature limit 
one has $q_0\to 1$, for any $\omega$. In particular, it is straightforward 
to check that  $q_0\approx 1-2(1-\omega)\exp(-2\beta^2)$ for $\beta\to\infty$.

@@

Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
${\mathcal I}_2$ in the infinite-range Ising model without disorder, i.e., the 
Curie-Weiss (CW) model, defined by the hamiltonian 
%
\begin{equation}
\label{is-clean}
{\mathcal H}=-\frac{J}{N}\sum\limits_{i<j}S_iS_j+h\sum_i S_i.
\end{equation}
%
We consider the situation without external magnetic field, i.e., $h=0$ and 
fix $J=1$. The phase diagram of the model exhibits a paramagnetic phase at 
high temperature, while at low temperatures there is ferromagnetic order. The 
two phases are separated by a phase transition at $\beta_c=1$.
We consider both the situations with finite $N$ as well as the 
thermodynamic limit. For finite $N$ we provide exact numerical results for 
$S_2$ and ${\mathcal I}_2$, while we address the thermodynamic limit using 
the booklet construction and the saddle point approximation.

Similar to the S-K model, we find that the para-ferro transition persists on 
the booklet, and the critical temperature depends on the booklet ratio 
$\omega$. The R\'enyi entropy $S_2$ and the mutual information ${\mathcal 
I}_2$ are extensive, and their densities $S_2/N,{\mathcal I}_2/N$ finite 
and smooth at any temperature. Notice that this in constrast with what is 
obtained for the von Neumann mutual information~\cite{wilms-2012} ${\mathcal I}$, 
which is {\it finite} (i.e., ${\mathcal I}\sim {\mathcal O}(1)$) in the whole phase 
diagram, except for a logarithmically divergent behavior at the critical 
point at $\beta_c=1$.

However, information about the phase transition is encoded in the subleading, 
i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, logarithmically 
divergent corrections are present at $\beta=1/2,1$ and $\beta=\beta_c(\omega)$, 
with $\beta_c(\omega)$ the critical temperature of the model on the booklet 
with aspect ratio $\omega$.

@@

The calculation of the booklet partition function $Z(\omega,n,\beta)$ 
(see section~\ref{booklet}) can be done using the same techniques as in 
section~\ref{the-model}. The result reads 
%
\begin{multline}
\label{clean-is-Z}
Z(\omega,n,\beta)=
\exp\Big(-\frac{\beta}{2}n\Big)\Big(2\pi\frac{\beta}{N}\Big)^{-\frac{n}{2}}
\int\prod_{\delta}dz_\delta\exp N\Big\{\\
-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
-(1-\omega)\log(2\cosh z_\delta)\Big]+\omega\log(2\cosh\sum_\delta z_\delta)
\Big\}.
\end{multline}
%
Using the saddle point approximation, from~\eqref{clean-is-Z} one obtains 
$F(\omega,n,\beta)\equiv\log Z(\omega,n,\beta)$ as 
%
\begin{multline}
\label{clean-is-F}
F(\omega,n,\beta)\approx
N\Big\{-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
-(1-\omega)\log(2\cosh z_\delta)\Big]\\
+\omega\log(2\cosh\sum_\delta z_\delta)\Big\}, 
\end{multline}
%
where we neglected subleading contributions $o(N)$. The parameters 
$\{z_\delta\}_{\delta=1}^n$ are solutions of the saddle point equations 
%
\begin{equation}
\label{clean-is-spe}
0=z_\delta-\beta(1-\omega)\tanh z_\delta-\beta\omega\tanh\big(\sum_\delta 
z_\delta\big),\quad \forall\delta.
\end{equation}
%
For $n=2$, the system~\eqref{clean-is-spe} becomes 
%
\begin{align}
& 0=z_1-\beta(1-\omega)\tanh z_1-\beta\omega\tanh\big(z_1+z_2\big)\\
& 0=z_2-\beta(1-\omega)\tanh z_2-\beta\omega\tanh\big(z_1+z_2\big). 
\end{align}
%
The system has the solutions $z_1=z_2=z_s=0$ for $\beta\le\beta_c=1/(1+\omega)$, 
and $z_1=z_2=z_s\ne 0$ for $\beta>\beta_c$. Note that $\beta_c$ is different 
in presence of disorder (compare with~\eqref{tc}).

The solution $z_s$ of the saddle point equations~\eqref{clean-is-spe} is shown 
in Fig.~\ref{saddle_clean} for $\omega=0,1/2,1$. The vertical-dotted line 
is $\beta_c$ for $\omega=1/2$. Notice that at low temperatures $z_s$ is 
independent on $\omega$, and one has $z_s\sim\beta$.

@@

It is straightforward to obtain the R\'enyi entropies $S_n=(F(\omega=0,n,\beta)-
F(\omega,n,\beta))/(n-1)$ using~\eqref{clean-is-F} and~\eqref{renyi}. 
Figure~\ref{renyi_clean} plots the entropy density $S_2/N$ versus the inverse 
temperature $\beta$. $S_2$ exhibits a volume-law behavior $S_2\propto N$ for 
all values of $\beta$ and $\omega$. The different curves correspond to different 
booklet aspect ratios $\omega$. Clearly, $S_2$ exhibits the volume-law behavior 
$S_2\propto N$ at all temperatures. For $\beta\le\beta_c$ one has the flat behavior 
$S_2=\omega\log(2)$, whereas $S_2$ is vanishing in the low-temperature regime. 
The full symbol (rhombi) in Figure~\ref{renyi_clean} are exact results for a 
booklet with $N=400$ spins per sheet (see next section), and are in good 
agreement with the saddle point approximation results.

The mutual information per spin ${\mathcal I}_2/N$ is reported in 
Figure~\ref{mi_clean}. The lines are the analytical results for booklet aspect 
ratios $\omega=1/20,1/4,1/2$, while the full symbols are the exact results for 
the booklet with $N=400$ spins per sheet. Clearly, ${\mathcal I}_2/N$ is exactly zero 
in the high-temperature region for $\beta\le1/2$, it exhibits at maximum 
at $\beta\approx 1$, and it is vanishing in the limit $\beta\to\infty$. 
Similar to Figure~\ref{reny_clean} the full symbols are exact results for 
a booklet with $N=400$ spins per sheet.

Notice that similar features are observed for the S-K model (see 
section~\ref{I2-section}). In particular, one should observe that ${\mathcal I}_2/N$ 
does not exhibit any crossing at the critical point $\beta_c$. However, the information 
about critical behavior is encoded in the finite-size corrections of ${\mathcal I}_2/N$ 
(see next section), which are neglected in the saddle point treatment. 
Finally, one should also stress that a dramatically different behavior is observed 
in the mutual information obtained from the von Neumann entropy ${\mathcal I}\equiv 
\lim_{n\to 1}{\mathcal I}_n$. Specifically, no volume law is present for ${\mathcal I}$, 
which, instead, exhibits a logarithmic divergence as ${\mathcal I}=1/4\log(N)$ at the 
critical point $\beta_c=1$ (see Ref.~\onlinecite{wilms-2012}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.9\linewidth]{./draft_figs/renyi_clean}
%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
\caption{ The infinite-range Ising model on the $2$-sheets booklet in the thermodynamic 
 limit: the classical R\'enyi entropy density $S_2/N$, with $N$ the total number of spins 
 on a single sheet of the booklet. $S_2/N$ is plotted against the inverse temperature 
 $\beta$ and for booklet aspect ratio $\omega=1/4,1/2,1$. Note tht at high temperature 
 $S_2=\omega\log(2)$. The full symbols denote the exact numerical results for a finite 
 system with $N=400$. 
}
\label{renyi_clean}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For finite number of spins $N$, $S_2$ and ${\mathcal I}_2$ can be calculated 
exactly using the results obtained in Ref.~\onlinecite{wilms-2012}. The eigenstates 
of~\eqref{is-clean} are product states. They can be characterized as $|p,i\rangle$, 
with $p$ the total number of up spins (the remaining $N-p$ being down) and $i$ 
labelling the $B(N,p)\equiv N!/(p!(N-p)!)$ eigenstates with the same $p$.

The partition function of the model is given as 
%
\begin{equation}
Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2},
\end{equation}
%
where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
Similarly, one has 
%
\begin{equation}
\label{rhon}
Z^n(\beta)\equiv\textrm{Tr}\rho^n=\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
\frac{1}{2})^2}. 
\end{equation}
%
Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
and $N-N_A$ spins, respectively, the reduced density matrix for $A$ is obtained 
as~\cite{wilms-2012} 
%
\begin{equation}
\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2}|p,i\rangle\langle p,i|. 
\end{equation}
%
By performing the trace over part $B$ one obtains 
%
\begin{equation}
\label{rhoA}
\rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
\end{equation}
%
where $|p_A,i_A\rangle$ form a basis for part $A$ of the system and 
%
\begin{equation}
R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{2N\beta
(\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
\end{equation}
%
From~\eqref{rhoA} it is straightforward to obtain 
%
\begin{equation}
\label{trrhoA}
\textrm{Tr}\rho_A^n=\sum\limits_{p_A=0}^{N_A}B(N_A,p_A)R^n(p_A). 
\end{equation}
%
Similarly, $\textrm{Tr}\rho^n_B$ is obtained from~\eqref{trrhoA} substituting 
$A\to B$ and $N_A\to N-N_A$, while $\textrm{Tr}\rho^n_{A\cup B}\equiv\textrm{Tr}
\rho^n$ is given in~\eqref{rhon}. The R\'enyi entropies $S_n$ and the mutual 
informations ${\mathcal I}_n$ can be numerically constructed numerically 
using~\eqref{trrhoA}, \eqref{rhon} and the definitions~\eqref{renyi-intro}
\eqref{MI}. The numerical results for $S_2$ and ${\mathcal I}_2$ for a system with 
$N=400$ spins are shown in Figure~\ref{renyi_clean} and Figure~\ref{mi_clean}, and 
are in good agreement with the saddle point results.

Figure~\ref{sp_corr} focuses on the finite-size corrections to the saddle point 
result for ${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with 
${\mathcal I}_2^{(sp)}$ denoting the saddle point results (see Figure~\ref{mi_clean}), 
versus $\beta$. We restrict ourselves to the situation with $\omega=N_A/N=1/2$, although 
similar resutls are expected at different $\omega$. Clearly, ${\mathcal I}_2-
{\mathcal I}_2^{(sp)}$ is vanishing at high temperature, whereas one has ${\mathcal I}_2-
{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit $\beta\to\infty$ (horizontal line). 
Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ diverges in the thermodynamic limit 
for $\beta=1/2,2/3,1$ (vertical lines in the Figure), which are the critical 
temperatures for the model on a booklet with $\omega=1,1/2,0$.

This divergence is logarithmic with $N$ as confirmed in Figure~\ref{clean_log} plotting 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
Interestingly, the precise behavior depends on $\beta$. Specificaly, one has 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/4\log(N)$ for $\beta=1/2$ and 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/2\log(N)$ for $\beta=2/3$ and 
$\beta=1$. Notice that this is dramatically different for the von Neumann mutual 
information ${\mathcal I}=\lim_{n\to 1}{\mathcal I}_n$, which exhibits only one 
divergent peak at $\beta=1$~\cite{wilms-2012}.

>>>>

In this section we present the solution of the S-K model on the booklet, using 
the replica symmetric (RS) approximation. In subsection~\ref{para-section} we focus 
on the high temperature phase, where this approximation is exact, and the 
behavior of the model is fully determined by the diagonal part of the overlap 
tensor $q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec} for its 
definition). In~\ref{shannon} we perform the analytic continuation $n\to 1$, 
which allows to obtain the Shannon mutual information $[{\mathcal I}_1]$. 
The generic structure of $q_{\gamma\gamma'}^{rr'}$ 
within the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us 
to determine the critical temperature of the paramagnetic-glassy transition. 
For simplicity, here and in the following sections we restrict ourselves to zero 
magnetic field ($h=0$ in Eq.~\eqref{SK-ham}), and to $J_0=0$ in 
Eq.~\eqref{quenched-distr}.

@@

\frac{\beta^2}{2}\Big(\frac{n}{2}-\frac{q_0^2}{2}(n^2-n)
+\omega q_0n^2-q_0n\Big)\\

@@

(\omega,n,\beta)]/\partial q_0=0$. $[F_{para}(\omega,n,\beta)]$ can be written in 
terms of simple functions using that 

@@

\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)=\\
\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\lfloor n/2\rfloor-1}\frac{\Gamma(n+1)}
{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0(n/2-k)^2}\\
+\frac{2^{-2\left\lfloor n/2\right\rfloor}\Gamma(n+1)}{\Gamma(n-\lfloor n/2\rfloor+1)
\Gamma(\lfloor n/2\rfloor+1)}e^{2\beta^2q_0(n/2-\lfloor n/2\rfloor)^2}, 
where $\Gamma(x)$ denotes the Euler Gamma function. 
The saddle point equation for $q_0$ reads 
\label{sp-g}
0=\beta\big(\omega n-1-q_0(n-1)\big)\\
+(1-\omega)\frac{\int Dz\cosh^{n-1}(z\sqrt{q_0}\beta)\sinh(z\sqrt{q_0}\beta)z}
{\sqrt{q_0}\int Dz\cosh^n(z\sqrt{q_0}\beta)}. 

@@

Clearly, for two independent copies of the S-K model, i.e., $\omega=0$,  
Eq.~\eqref{saddle-high-t} gives $q_0=0$ for $\beta\le1$, whereas 
one has $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$, $q_0$ 
is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle_ht}. For $\beta=0$ it 
is $q_0=\omega$ (straight line in the Figure). In the low-temperature limit 
one has $q_0\to 1$, for any $\omega$. In particular, it is straightforward 
to check that  $q_0\approx 1-2(1-\omega)\exp(-2\beta^2)$ for $\beta\to\infty$.

%##########################################################################
\subsection{The analytic continuation $n\to 1$}
\label{shannon}

It is interesting to consider the analytic continuation $\lim_{n\to 1} [S_n]$ 
and $\lim_{n\to 1}[{\mathcal I}_n]$ to obtain the Shannon entropy and mutual 
information. In the limit $n\to 1$, $F_{para}(\omega,n,\beta)$ (see~\eqref{ht-logZ}) 
does not depend on $q_0$ and $\omega$,  as expected. This holds for any 
$\beta$ even including the effects of the replica symmetry breaking. However, 
the Shannon entropy $S_1(A)$ (and the mutual information ${\mathcal I}_1$ thereof) 
is non trivial due to the prefactor $1/(1-n)$ in~\eqref{renyi}. In order to 
obtain $S_1(A)$ one should consider $1/(1-n)[F_{para}(\omega,n,\beta)]$ 
performing carefully the limit $n\to 1$. The result reads 
%
\begin{multline}
\label{sh-F}
\frac{[F_{para}(\omega,1,\beta)]}{N(1-n)}=
\omega\log(2)+
\frac{\beta^2}{2}\Big(\frac{q_0^2}{2}n
-\omega q_0(n+1)+q_0\Big)\\
-(1-\omega)\frac{\int Dz\cosh(z\sqrt{q_0}\beta)
\log\cosh(z\sqrt{q_0}\beta)}{\int Dz\cosh(z\sqrt{q_0\beta})}. 
\end{multline}
%
The saddle point equation~\eqref{sp-g} for $q_0$ now becomes  
%
\begin{multline}
(\omega-q_0)\exp\big(\beta^2\frac{q_0}{2}\big)
+(1-\omega)\int Dz\Big(\frac{z}{\beta\sqrt{q_0}}\sinh(z\sqrt{q_0}\beta)\\
-\cosh(z\sqrt{q_0}\beta)\Big)\log\cosh(z\sqrt{q_0}\beta)=0. 
\end{multline}
%
Notice that in the limit $\beta\to 0$ one has $q_0\to\omega$, which implies,   
using~\eqref{sh-F} and~\eqref{MI}, the volume-law behavior $[{\mathcal I}_1]
\to\beta^2/2\omega(1-\omega)N$. This in constrast with the clean 
case~\cite{wilms-2012}, where ${\mathcal I}_1={\mathcal O}(1)$ for any 
$\beta$ away from the critical point at $\beta_c=1$.

@@

Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
${\mathcal I}_2$ in the infinite-range Ising model without disorder, defined by 
the hamiltonian 
%
\begin{equation}
\label{is-clean}
{\mathcal H}=-\frac{J}{N}\sum\limits_{i<j}S_iS_j+h\sum_i S_i.
\end{equation}
%
We consider the situation without external magnetic field, i.e., $h=0$ and 
fix $J=1$. The phase diagram of the model exhibits a paramagnetic phase at 
high temperature, while at low temperatures there is ferromagnetic order. The 
two phases are separated by a phase transition at $\beta_c=1$.
We consider both the situations with finite $N$ as well as the 
thermodynamic limit. For finite $N$ we provide exact numerical results for 
$S_2$ and ${\mathcal I}_2$, while we address the thermodynamic limit using 
the booklet construction (see~\ref{booklet}) and the saddle point 
approximation.

Similar to the S-K model, we find that the para-ferro transition persists on 
the booklet, and the critical temperature depends on the booklet ratio 
$\omega$. The R\'enyi entropy $S_2$ and the mutual information ${\mathcal 
I}_2$ are extensive, and their densities $S_2/N,{\mathcal I}_2/N$ finite 
and smooth at any temperature. Notice that this different for the Shannon 
mutual information~\cite{wilms-2012} ${\mathcal I}_1$, which is {\it finite} 
(i.e., ${\mathcal I}_1\sim {\mathcal O}(1)$) in the whole phase diagram, 
except for a logarithmically divergent behavior (with system size) at the 
critical point $\beta_c=1$.

Finally, we show that the information about the phase transition is encoded in 
the subleading, i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, 
logarithmically divergent contributions are present at $\beta=1/2,1$ and 
$\beta=\beta_c(\omega)$, with $\beta_c(\omega)$ the critical temperature of the 
model on the booklet at fixed aspect ratio $\omega$.

@@

We first discuss the thermodynamic limit. The calculation of the booklet partition 
function $Z(\omega,n,\beta)$ (see section~\ref{booklet}) can be done using the same 
techniques as in section~\ref{the-model}. The result reads 
%
\begin{multline}
\label{clean-is-Z}
Z(\omega,n,\beta)=
\exp\Big(-\frac{\beta}{2}n\Big)\Big(2\pi\frac{\beta}{N}\Big)^{-\frac{n}{2}}
\int\prod_{\delta}dz_\delta\exp N\Big\{\\
-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
-(1-\omega)\log(2\cosh z_\delta)\Big]+\omega\log(2\cosh\sum_\delta z_\delta)
\Big\}, 
\end{multline}
%
with $\delta=1,\dots,n$. Using the saddle point approximation, from~\eqref{clean-is-Z} 
one obtains $F(\omega,n,\beta)\equiv\log Z(\omega,n,\beta)$ as 
%
\begin{multline}
\label{clean-is-F}
F(\omega,n,\beta)\approx
N\Big\{-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
-(1-\omega)\log(2\cosh z_\delta)\Big]\\
+\omega\log(2\cosh\sum_\delta z_\delta)\Big\}, 
\end{multline}
%
where we neglected subleading contributions $o(N)$. The parameters 
$\{z_\delta\}_{\delta=1}^n$ are solutions of the saddle point equations 
%
\begin{equation}
\label{clean-is-spe}
0=z_\delta-\beta(1-\omega)\tanh z_\delta-\beta\omega\tanh\big(\sum_\delta 
z_\delta\big),\quad \forall\delta.
\end{equation}
%
For $n=2$, the system~\eqref{clean-is-spe} becomes 
%
\begin{align}
& 0=z_1-\beta(1-\omega)\tanh z_1-\beta\omega\tanh\big(z_1+z_2\big)\\
& 0=z_2-\beta(1-\omega)\tanh z_2-\beta\omega\tanh\big(z_1+z_2\big). 
\end{align}
%
The system has the solutions $z_1=z_2=z_s=0$ for $\beta\le\beta_c=1/(1+\omega)$, 
and $z_1=z_2=z_s\ne 0$ for $\beta>\beta_c$. Note that $\beta_c$ is different 
in presence of disorder (see~\eqref{tc}).

The solution $z_s$ of the saddle point equations~\eqref{clean-is-spe} is shown 
in Fig.~\ref{saddle_clean} as a function of $\beta$ for $\omega=0,1/2,1$. 
The vertical-dotted line is $\beta_c$ for $\omega=1/2$. Notice that at low 
temperatures $z_s$ is independent on $\omega$, and one has $z_s\sim\beta$.

@@

It is straightforward to obtain the R\'enyi entropies $S_n=(F(\omega=0,n,\beta)-
F(\omega,n,\beta))/(n-1)$ using~\eqref{clean-is-F} and~\eqref{renyi}. 
Figure~\ref{renyi_clean} plots the entropy density $S_2/N$ versus the inverse 
temperature $\beta$. $S_2$ exhibits a volume-law behavior $S_2\propto N$ for 
all values of $\beta$ and $\omega$. The different curves correspond to different 
booklet aspect ratios $\omega$. For $\beta\le\beta_c$ one has the flat behavior 
$S_2=\omega\log(2)$, whereas $S_2$ is vanishing in the low-temperature regime. 
The full symbol (rhombi) in Figure~\ref{renyi_clean} are exact results for a 
booklet with $N=400$ spins per sheet (see next section), and are in good 
agreement with the saddle point approximation results.

The mutual information per spin ${\mathcal I}_2/N$ is reported in 
Figure~\ref{mi_clean}. The lines are the analytical results for booklet aspect 
ratios $\omega=1/20,1/4,1/2$, while the full symbols are the exact results for 
the booklet with $N=400$ spins per sheet. Clearly, ${\mathcal I}_2/N$ is exactly zero 
in the high-temperature region for $\beta\le1/2$, it exhibits at maximum 
at $\beta\approx 1$, and it is vanishing in the limit $\beta\to\infty$.

Finally, one should stress that a dramatically different behavior is observed 
in the Shannon mutual information ${\mathcal I}_1\equiv \lim_{n\to 1}{\mathcal I}_n$. 
Specifically, ${\mathcal I}_1$ is finite in the thermodynamic limit, and it only 
exhibits a logarithmic divergence as ${\mathcal I}=1/4\log(N)$ at the 
critical point $\beta_c=1$ (see Ref.~\onlinecite{wilms-2012}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.9\linewidth]{./draft_figs/renyi_clean}
%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
\caption{ The infinite-range Ising model on the $2$-sheets booklet in the thermodynamic 
 limit: the classical R\'enyi entropy density $S_2/N$, with $N$ the total number of spins 
 on a single sheet of the booklet. $S_2/N$ is plotted against the inverse temperature 
 $\beta$ and for booklet aspect ratio $\omega=1/4,1/2,1$. Note tht at high temperature 
 $S_2=\omega\log(2)$. The lines are obtained using the saddle point approximation, while 
 the full symbols denote the exact numerical results for a finite system with $N=400$. 
}
\label{renyi_clean}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For finite $N$, $S_2$ and ${\mathcal I}_2$ can be calculated exactly using the 
results obtained in Ref.~\onlinecite{wilms-2012}. The eigenstates 
of~\eqref{is-clean} are product states. They can be characterized as $|p,i\rangle$, 
with $p$ the total number of up spins (the remaining $N-p$ being down spins) and $i$ 
labelling the $B(N,p)\equiv N!/(p!(N-p)!)$ eigenstates with the same $p$. 
The partition function of~\eqref{is-clean} is given as 
%
\begin{equation}
Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2}.
\end{equation}
%
Similarly, one has 
%
\begin{equation}
\label{rhon}
Z^n(\beta)\equiv\textrm{Tr}\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
\frac{1}{2})^2}. 
\end{equation}
%
The thermal density matrix $\rho$ is defined as $\rho\equiv 1/Ze^{-\beta{\mathcal H}}$. 
Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
and $N-N_A$ spins, respectively, the reduced density matrix for $A$ is obtained 
as~\cite{wilms-2012} 
%
\begin{equation}
\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2}|p,i\rangle\langle p,i|. 
\end{equation}
%
By performing the trace over part $B$ one obtains 
%
\begin{equation}
\label{rhoA}
\rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
\end{equation}
%
where $|p_A,i_A\rangle$ form a basis for part $A$ of the system and 
%
\begin{equation}
R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{2N\beta
(\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
\end{equation}
%
From~\eqref{rhoA} it is straightforward to obtain 
%
\begin{equation}
\label{trrhoA}
\textrm{Tr}\rho_A^n=\sum\limits_{p_A=0}^{N_A}B(N_A,p_A)R^n(p_A). 
\end{equation}
%
Similarly, $\textrm{Tr}\rho^n_B$ is obtained from~\eqref{trrhoA} substituting 
$A\to B$ and $N_A\to N-N_A$, while $\textrm{Tr}\rho^n_{A\cup B}\equiv\textrm{Tr}
\rho^n$. The R\'enyi entropies $S_n$ and the mutual 
informations ${\mathcal I}_n$ can be calculated numerically 
using~\eqref{trrhoA}, \eqref{rhon} and the definitions~\eqref{renyi-intro}
\eqref{MI}. The numerical results for $S_2$ and ${\mathcal I}_2$ for a system with 
$N=400$ spins are shown in Figure~\ref{renyi_clean} and Figure~\ref{mi_clean}, and 
are in good agreement with the results in the thermodynamic limit.

Figure~\ref{sp_corr} focuses on the finite-size subextensive corrections for 
${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with ${\mathcal I}_2^{(sp)}$ 
denoting the saddle point extensive part of ${\mathcal I}_2$. We restrict ourselves to 
$\omega=N_A/N=1/2$, although similar results have to be expected at different $\omega$. 
Clearly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ is vanishing at high temperatures, 
whereas one has ${\mathcal I}_2-{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit 
$\beta\to\infty$ (horizontal line). Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ 
diverges in the thermodynamic limit for $\beta=1/2,2/3,1$ (vertical lines in the 
Figure), which are the critical temperatures for the model on a booklet with 
$\omega=1,1/2,0$. 
This divergence is logarithmic as a function of $N$, as confirmed in Figure~\ref{clean_log} 
plotting $|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
Interestingly, the precise behavior depends on $\beta$. One has 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/4\log(N)$ for $\beta=1/2$ and 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/2\log(N)$ for $\beta=2/3$ and 
$\beta=1$. Again, this is dramatically different for the von Neumann mutual 
information ${\mathcal I}=\lim_{n\to 1}{\mathcal I}_n$, which exhibits only one 
divergent peak~\cite{wilms-2012} at $\beta=1$.
